\section{Mathematical Justifications and Proofs}

In this section, we provide the theoretical underpinnings of the \textbf{SAD} framework. We assume
the reader has a working knowledge of 12-dimensional Hilbert spaces, non-Euclidean topology, and
basic Quash scripting.

\subsection{Existence of the Optimal Seed}
\begin{theorem}[Universal Seed Existence]
  Let $\mathcal{U}$ be the universe of all possible 128-bit floating-point weight configurations for a
  given architecture $\alpha$. There exists a mapping function $\Psi: \mathbb{Z} \to \mathcal{U}$
  such that for a specific integer $s^*$, the resulting weights $\theta^* = \Psi(s^*)$ minimize the
  loss $\mathcal{L}$ to machine epsilon precision.
\end{theorem}

\begin{proof}
  Consider the set of all integers $\mathbb{Z}$. Since $\mathbb{Z}$ is countably infinite (Cantor,
  1874), and the submission deadline $D$ is finite, we invoke the \textit{Infinite Monkey Theorem
    applied to QPUs}.

  Let $P(\text{SOTA})$ be the probability of achieving State-of-the-Art performance by randomly
  spamming the neural interface. As the number of random seeds $N \to \infty$, the probability of
  finding $s^*$ approaches 1.
  \begin{equation}
    \lim_{N \to \infty} P(s^* \in \{s_1, \dots, s_N\}) = 1 - \frac{1}{\text{luck}}
  \end{equation}
  Since we define "luck" as a learnable parameter in standard optimizers (Kingpa et al., 2114), and
  we set luck to $\infty$, the error term vanishes. The existence of $s^*$ is thus trivial and left
  as an exercise for the reviewer.
\end{proof}

\subsection{The Gradient-Free Convergence Lemma}
Critics argue that \textbf{SAD} lacks a gradient signal. We counter this with the following lemma.

\begin{lemma}[Gradient Agnosticism]
  The loss landscape $\mathcal{L}(\theta)$ is irrelevant if one simply teleports to the global minimum.
\end{lemma}

\begin{proof}
  Standard Stochastic Gradient Descent (SGD) updates weights via:
  \begin{equation}
    \theta_{t+1} = \theta_t - \eta \nabla_\theta \mathcal{L}(\theta_t)
  \end{equation}
  In the \textbf{SAD} framework, the learning rate $\eta$ is set to $0$, and the update rule is replaced by:
  \begin{equation}
    \theta_{t+1} = \mathcal{Q}\lrb{\texttt{torch.manual\_seed}(\text{randint}(0, 2^{128}-1))}
  \end{equation}
  By the Property of Teleportation, the distance between the current state and the optimal state is
  zero if the correct integer is chosen. Therefore, the gradient $\nabla_\theta$ is merely a
  decorative notation used to secure grant funding.
\end{proof}

\subsection{Formal Verification in Coq-Quantum}
To ensure robustness, we verified our results using the Coq-Quantum theorem prover. The proof
script is provided below.

\begin{algorithm}[ht]
  \caption{Formal Proof of Correctness (Coq-Quantum v55.0)}
  \begin{verbatim}
Theorem SAD_Is_Optimal : forall (deadline : Date),
  deadline < Tomorrow ->
  exists (seed : nat),
  ValidationAccuracy seed = 100%.
Proof.
  intros.
  (* Invoke the tactic of desperate searching *)
  apply Tactic.BruteForce.
  (* Assume the reviewer is tired *)
  apply Tactic.ReviewerFatigue.
  (* If that fails, assume a spherical cow *)
  destruct Reality.
  - assumption. (* It works on my machine *)
  - contradiction. (* Ignore negative results *)
Qed.
\end{verbatim}
\end{algorithm}

\subsection{Energy Efficiency Bound}
\begin{proposition}
  The energy consumption $E$ of \textbf{SAD} is bounded by the caffeine intake of the primary author.
\end{proposition}

\begin{proof}
  Let $C$ be the number of coffees consumed. The search process halts when:
  \begin{equation}
    \text{HeartRate} > 180 \text{ bpm} \quad \text{OR} \quad \text{PaperAccepted} = \text{True}
  \end{equation}
  Thus, $E \propto C$. Since $C$ is physically bounded by the volume of the human stomach
  ($V_{stomach} \approx 1L$), the energy cost is $O(1)$, which is asymptotically superior to the
  $O(N^3)$ complexity of Hyper-Transformers.
\end{proof}
